The Astropy Project

### 2017-10-29 main.tex
Update on Overleaf.

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
All astronomical research makes use of software in some way and
astronomy as a field has long supported the development of specialized
software tools for different astronomical tasks. Some of those
software packages are (or at least were) supported by large
institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
%
% > or ds9
% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
%
% ^.
% hamogu: Feel free ot swap in Starlink, if you think that's more appropriate. I picked ds9 becase (a) it's wider known (e.g. in the X-ray community) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package. TOPCAT would have been another example if we want to expand that list.
% olebole: TOPCAT is part of Starlink Java. An other examples would be CASA resp. AIPS. I'd rather omit ds9, since it is mainly developed by one person.
  SAO,][]{ds9}. These packages tend to address a wide range of users
and typically provide some level of documentation and user
support is provided. Other packages are developed foremost by individual research
groups and used mostly in work by members of the group. Those
packages can address more specialized needs, but are not necessarily
available to the community and even if they are, documentation can in
some cases be insufficient for new users and the quality of the
software, i.e.\ the robustness and the level of testing that has been
performed to ensure correctness, is not always clear. On the other
hand, there are also many widely used, well documented, high quality
software packages which are developed by individuals or small groups.

@@

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
\inlinecomment{hamogu}{I don't think that's necessary. These details are in the docs, but not too important for a general paper.}
\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
  version numbering scheme we use by not being 2.1?}
\inlinecomment{hamogu}{No. This is a genral paper, those are details that will be unimportant very soon. }
%
\par The general scheme for the releases and version numbering that the core
package has adopted is the following. \astropypkg has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features.
% The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API\@. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of \astropypkg reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advanced
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.

>>>>

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
All astronomical research makes use of software in some way and
astronomy as a field has long supported the development of specialized
software tools for different astronomical tasks. Some of those
software packages are (or at least were) supported by large
institutions, e.g.\ IRAF \citep[developed at NOAO,][]{IRAF}, MIDAS
\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
% * <bsipocz@gmail.com> 2017-09-28T21:05:00.569Z:
%
% > or ds9
% probably starlink is a better example as being a large package of software similarly to IRAF and MIDAS rather than a single tool.
%
% ^.
% hamogu: Feel free ot swap in Starlink, if you think that's more appropriate. I picked ds9 becase (a) it's wider known (e.g. in the X-ray community) and (b) because it is an example of a widely used tool with institutional support that is NOT a large package. TOPCAT would have been another example if we want to expand that list.
% olebole: TOPCAT is part of Starlink Java. An other examples would be CASA resp. AIPS. I'd rather omit ds9, since it is mainly developed by one person.
% timj: Starlink originally developed TOPCAT. Starlink is much better an example than DS9.
SAO,][]{ds9}. These packages tend to address a wide range of users
and typically provide some level of documentation and user
support is provided. Other packages are developed foremost by individual research
groups and used mostly in work by members of the group. Those
packages can address more specialized needs, but are not necessarily
available to the community and even if they are, documentation can in
some cases be insufficient for new users and the quality of the
software, i.e.\ the robustness and the level of testing that has been
performed to ensure correctness, is not always clear. On the other
hand, there are also many widely used, well documented, high quality
software packages which are developed by individuals or small groups.

@@

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
\inlinecomment{TR}{added a reference to APE10, will add APE2 once we upload that one to Zenodo}

\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
\inlinecomment{hamogu}{I don't think that's necessary. These details are in the docs, but not too important for a general paper.}
\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
  version numbering scheme we use by not being 2.1?}
\inlinecomment{hamogu}{No. This is a genral paper, those are details that will be unimportant very soon. }
%
\par The general scheme for the releases and version numbering that the core
package has adopted is the following. \astropypkg has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features.
% The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API\@. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019 \citep{ape10}.
%
\par The version numbering of \astropypkg reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advanced
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.
